\huge A Usability Evaluation of Tor Launcher

### 2017-03-15 pets2017-paper/pets2017-paper.tex
wordsmith procedure and recruitment for formatting

\subsection{Recruitment}
We recruited 59 participants from the Xlab mailing list, which is a university-wide pool of participants who have opted-in to participating in social science experiments (see Appendix~\ref{quantitative-recruitment} for the recruitment materials). We recruited an additional 65 participants from Craigslist to ensure diversity, since Xlab participants are primarily students and staff from UC Berkeley.

Of our 124 participants, we filtered out 10 participants who did not complete the consent form correctly or did not interact with the interface. One participant did not report their demographics, but we still used their data. Of the remaining 113, 44.2\% identified as male, 54.0\% identified as female, and 1.8\% identified as neither. They were between 18 and~68 years old ($\mu = 28.2$, $\sigma = 12.3$) and highly educated (84.1\% had at least a college education).

\subsection{Procedure}
We ran our experiment at the Xlab~\cite{xlab}, an experimental social science laboratory. The room had 36 workstations with identical Windows~7 laptops. Workstation partitions discouraged participants from looking at other screens. We automatically reverted the computers to the same image at the beginning of each session. Before each session, we ran a script that downloaded the necessary software (Firefox, Chrome, Internet Explorer, VLC media player, and Tor Browser 5.0.3 with or without our proposed UI changes), set up one of the three simulated environments (E1, E2, or E3), and started the computer screen recording. We instrumented Tor Browser to log user interactions. We manually assigned each computer to one of the six interface--environment combinations in a way that evenly distributed experimental conditions throughout the room.

We assigned participants to a simulated censorship environment combination at random by assigning them to a computer at random. We informed participants that they were in a simulated censorship environment, informed them that Tor browser was necessary to circumvent censorship, and pointed out that Tor was installed for them on the computer (Appendix~\ref{quantitative-script}). We asked them to complete a worksheet that required visiting a censored site (Wikipedia) and explicitly reminded them to use Tor to do so (Appendix~\ref{summative-worksheet}). Before the experiment began, we reminded them that we were recording their screens, answered any questions, then gave them 40 minutes to complete the task.

Researchers maintained minimal interactions with the participants after instructions, only answering logistical questions. After the experiment and exit survey (Appendix~\ref{quantitative-exit-survey}), we answered any additional questions and gave them \$30.

>>>>

\subsection{Recruitment}
We recruited 59 participants from the Xlab mailing list, which is a university-wide pool of participants who have opted-in to participating in social science experiments (see Appendix~\ref{quantitative-recruitment} for recruitment materials). We recruited an additional 65 participants from Craigslist to ensure diversity, since Xlab participants are primarily students and staff from UC Berkeley.

Of our 124 participants, we filtered out 10 participants who did not complete the consent form correctly or downloaded another version of Tor Browser to use during the experiment. One participant did not report their demographics, but we still used their data. Of the remaining 113, 44.2\% identified as male, 54.0\% as female, and 1.8\% as neither. They were between 18 and~68 years old ($\mu = 28.2$, $\sigma = 12.3$) and highly educated (84.1\% had at least a college education).

\subsection{Procedure}
We ran our experiment at Xlab~\cite{xlab}, an experimental social science laboratory. Xlab had 36 workstations with identical Windows~7 laptops, with workstation partitions to discourage participants from looking at other screens. At the beginning of each session, we used a script to revert the computers to a clean image, download Firefox, Chrome, Internet Explorer, VLC media player, and Tor Browser 5.0.3 (instrumented versions that logged user interactions, with/without our proposed UI changes ), set up one of the three simulated environments (E1, E2, or E3), and started recording the computer screen. We manually assigned interface--environment combinations to each computer.

We receive informed consent after talking about the study (Appendix~\ref{quantitative-script}) and instruct participants to use Tor to complete their worksheet (Appendix~\ref{summative-worksheet}), and gave them 40 minutes to complete the task. Researchers maintained minimal interactions with the participants. After the experiment and exit survey (Appendix~\ref{quantitative-exit-survey}), gave them \$30 for their time.
